Historical trends in the contribution of six major causes of death to the black-white

### 2017-04-26 Manuscript/Manuscript_COD_Trends.Rmd

Injury is one of the least common causes of death. Over time, injury-related mortality has decreased precipitously among blacks, although an [insurgence][*better word?*] of crime resulted in heightened mortality from injuries among black males during the 1990s (**eFigure X**). For whites, most states exhibit an initial period of gradual decreases in injury mortality, followed by a period of gradual increases, especially among white females (**eFigure X**). Thus, injury mortality rates among blacks are the same as, or lower than those among whites in many states, with white females demonstrating sharper increases. Thus, the contribution of injuries to the mortality gap has generally decreased over time, and has become negative in those states with lower injury-related mortality among blacks than whites (**Figures 9 and 10**). Among males, DC, Illinois, Michigan and Missouri exhibit the largest recent injury-related contributions. Among females, many southern states exhibit negative contributions (indicating lower injury-related mortality among black women), while DC, Illinois, and Michigan having higher contributions than the general trend.

>>>>

Injury is one of the least common causes of death. Over time, injury-related mortality has decreased precipitously among blacks, although an [insurgence][better word?] of crime resulted in heightened mortality from injuries among black males during the 1990s (**eFigure 7**). For whites, most states exhibit an initial period of gradual decreases in injury mortality, followed by a period of gradual increases, especially among white females (**eFigure 8**). Thus, injury mortality rates among blacks are the same as, or lower than those among whites in many states, with white females demonstrating sharper increases. Thus, the contribution of injuries to the mortality gap has generally decreased over time, and has become negative in those states with lower injury-related mortality among blacks than whites (**Figures 9 and 10**). Among males, DC, Illinois, Michigan and Missouri exhibit the largest recent injury-related contributions. Among females, many southern states exhibit negative contributions (indicating lower injury-related mortality among black women), while DC, Illinois, and Michigan having higher contributions than the general trend.
